Inefficient Concessions and Mediation

### 2021-01-17 notes.tex
fix min dh for e=0 case in calculations file
clean up mediator case to-do list

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
						\begin{itemize}
							\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE.
							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
							\item \textbf{Find the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote}
								\begin{itemize}
									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)?
										\begin{itemize}
											\item No, it's not possible. Asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
											\item I still don't have intuition for the asymptote. Need to look back at IC constraint to get it.
										\end{itemize}
								\end{itemize}
						\end{itemize}
					\item Ideally would want to combine $WM > W0$ and $WM > W1$ to get WM = max$\left\{WM, W1,W0\right\}$
						\begin{itemize}
							\item I basically CAN do this with asymptote conditions...or at least try
						\end{itemize}
					\item Maybe I can just do comparative statics on the condition? \url{http://people.duke.edu/~dgraham/scripts/MathematicaLaTeX-to-LaTeX/ComparativeStatics-none.pdf}
					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
						\[
						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
						\]
						\[
						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
						\]
						\[
						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
						\]
						\[
						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
						\]
						\[
						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
						\]
						I have a page of math that shows that this is strictly smaller than $d^h$. This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.
							\begin{itemize}
								\item This is nice, but I'm not sure it helps with the narrative of the story.
							\end{itemize}
			\end{itemize}

>>>>

\subsubsection{To do and Notes}		
	\color{ForestGreen} 
			\begin{itemize}
					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
						\begin{itemize}
							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator? YES
							\item \textbf{Find the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote}
								\begin{itemize}
									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)?
										\begin{itemize}
											\item No, it's not possible. Asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
										\end{itemize}
									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
										\[
											\frac{e p T}{1 - \de_h} > 1
										\]
										\begin{itemize}
											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
										\end{itemize}
								\end{itemize}
						\end{itemize}
					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
						\[
						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
						\]
						\[
						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
						\]
						\[
						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
						\]
						\[
						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
						\]
						\[
						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
						\]
						\[
							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
						\]
							\begin{itemize}
								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
							\end{itemize}
						The following shows that this is strictly smaller than $\de^h$. This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.
							\begin{itemize}
								\item $T+D>W$
								\item $-(T+D)<-W$
								\item $-p(T+D)<-pW$
								\item $W-p(T+D)<W-pW$
								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
								\item This is nice, but I'm not sure it helps with the narrative of the story.
							\end{itemize}
			\end{itemize}
